### 2019-07-25 5_evaluation.tex
More work shrinking space.

Figure~\ref{fig:bytes} shows the performance of Task Bench
implementations with a memory-bound kernel. We measure peak memory
bandwidth of 108~GB/s, which compares favorably with the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} which report up to 98~GB/s.

@@

One of the basic questions when considering different programming
systems is: How much overhead does the system add? This question is tricky to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, Realm, and Regent,
support both configurations.

@@

The least complicated pattern (stencil) is most favorable
to MPI, as it provides no
opportunity for task parallelism. For the stencil pattern, the
dominating factor is the basic overhead of executing a task, which is
minimal for MPI as the Task Bench implementation simply executes tasks one after another in alternation with
communication phases. In contrast, the asynchronous execution
mechanisms of other systems are pure overhead in this scenario.

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs.

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependencies, as the higher overheads of these systems require
unreasonably large problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency.

@@

METG is a useful metric in part because it summarizes the basic task
scheduling overhead of each programming system in a single number. This makes it
possible to evaluate METG at different node counts (shown in
Figure~\ref{fig:metg-compute}) to see how it is impacted by changes in
communication topology and latency. A key finding is that
the systems with the smallest METG on one node have roughly an order
of magnitude higher METG at 256 nodes---increased communication latencies require significantly larger tasks to
achieve the same level of efficiency, so apparent differences in
runtime overhead at small node counts can matter much less or not at
all at larger node counts.

@@

Asynchronous systems such as Charm++ are able to show two benefits in
these plots. First, by overlapping communication with computation,
such systems execute smaller task granularities at higher
levels of efficiency compared to the bulk synchronous MPI
implementation. Second, the asynchrony and scheduling flexibility from
executing multiple graphs also makes the curves smoother,
as spikes in latency due to interference from other jobs can be
mitigated, leading to more predictable performance, especially at
smaller message sizes.

@@

Figure~\ref{fig:cuda-efficiency} shows a comparison between the MPI
and MPI+CUDA implementations on the Piz Daint supercomputer. The CUDA
compute kernel achieves a peak performance of $4.759 \times 10^{12}$
FLOP/s, which is very close to the officially reported number
$4.761 \times 10^{12}$. The CPU kernel achieves $5.726 \times 10^{11}$
FLOP/s. Note that the CPU and GPU kernels perform different numbers of
operations as the GPU must be given more work to achieve peak
performance. The x-axis in Figure~\ref{fig:cuda-efficiency} has been
normalized so that the number of FLOPs is constant for a given problem
size.

>>>>

Figure~\ref{fig:bytes} shows performance with a memory-bound kernel. We measure peak memory
bandwidth of 108~GB/s, which compares favorably with the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} which report up to 98~GB/s.

@@

One question when considering different programming
systems is: How much overhead does the system add? This question is tricky to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, Realm, and Regent,
support both configurations.

@@

The least complicated pattern (stencil) is most favorable
to MPI, as it provides no
opportunity for task parallelism. For the stencil pattern, the
dominating factor is the basic overhead of executing a task, which is
minimal for MPI as the Task Bench implementation simply executes tasks one after another in alternation with
communication phases. In contrast, the asynchronous execution
mechanisms of other systems are pure overhead in this scenario.
The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs.

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependencies, as the overheads of these systems require
excessive problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency.

@@

METG is useful in part because it summarizes the overhead of each programming system in a single number. This makes it
possible to evaluate METG at different node counts (shown in
Figure~\ref{fig:metg-compute}) to see how it is impacted by changes in
communication topology and latency. A key finding is that
the systems with the smallest METG on one node have roughly an order
of magnitude higher METG at 256 nodes---increased communication latencies require significantly larger tasks to
achieve the same level of efficiency, so apparent differences in
runtime overhead at small node counts can matter much less or not at
all at larger node counts.

@@

Asynchronous systems such as Charm++ demonstrate two benefits in
these plots. First, by overlapping communication with computation,
such systems execute smaller task granularities at higher
levels of efficiency compared to the MPI
implementations. Second, the asynchrony and scheduling flexibility from
executing multiple graphs also makes the curves smoother,
as spikes in latency due to interference from other jobs can be
mitigated, leading to more predictable performance, especially at
smaller message sizes.

@@

Figure~\ref{fig:cuda-efficiency} compares MPI
and MPI+CUDA on the Piz Daint supercomputer. The CUDA
compute kernel achieves a peak performance of $4.759 \times 10^{12}$
FLOP/s, which is very close to the officially reported number
$4.761 \times 10^{12}$. The CPU kernel achieves $5.726 \times 10^{11}$
FLOP/s. Note that the CPU and GPU kernels perform different numbers of
operations as the GPU must be given more work to achieve peak
performance. The x-axis in Figure~\ref{fig:cuda-efficiency} has been
normalized so that the number of FLOPs is constant for a given problem
size.

### 2019-07-25 7_conclusion.tex
Apply Alex's comments.
More work shrinking space.

\item Systems that support asynchronous execution show benefits under
  load imbalanced workloads, or workloads with balanced computation
  and communication. However, these gains can be easily nullified by
  high baseline overheads.

@@

We have implemented Task Bench for a broad set of programming systems
spanning large scale data analytics and HPC. However, there are
systems not represented in our evaluation that would be interesting to
consider in the future. These include GASNet~\cite{GASNET07},
Habanero~\cite{Habanero11}, Hadoop~\cite{Hadoop},
HPX~\cite{Kaiser2014}, Nimbus~\cite{Nimbus17}, OCR~\cite{OCR14},
OpenSHMEM~\cite{OpenSHMEM10}, Ray~\cite{Ray18}, and UPC~\cite{UPC99}.

>>>>

\item Systems that support asynchronous execution show benefits under
  load imbalanced workloads, or workloads with balanced computation
  and communication. However, these gains can be nullified by
  high baseline overheads.

@@

\zap{
We have implemented Task Bench for a broad set of programming systems
spanning large scale data analytics and HPC. However, there are
systems not represented in our evaluation that would be interesting to
consider in the future. These include GASNet~\cite{GASNET07},
Habanero~\cite{Habanero11}, Hadoop~\cite{Hadoop},
HPX~\cite{Kaiser2014}, Nimbus~\cite{Nimbus17}, OCR~\cite{OCR14},
OpenSHMEM~\cite{OpenSHMEM10}, Ray~\cite{Ray18}, and UPC~\cite{UPC99}.
} % zap
